ManuscriptFigures

### 2024-01-30 Code/ManuscriptFigures.Rmd
Fixed wrong color assignment in figures. Added fig caption

MyWavelengths = c("WW", 660, 530, 450)

MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))

@@

```{r PURPARRatioPlots, fig.height= 10, fig.width= 10}

PurParPlot <- PURPARFits %>%
  filter(Par_ue %in% c(30, 90, 180)) %>%
  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>% 
  ggplot() +
  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = Pur_ue,colour = as.factor(WL)), linewidth = 0.7) +
    geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
  labs(y = "PUR (µE)" , x = "PAR (µE)") +
   scale_x_continuous(breaks=seq(0, 180, by = 30)) +
  # coord_cartesian(xlim = c (0, 180)) +
    scale_y_continuous(breaks=seq(0, 180, by = 30)) +
  coord_fixed(ylim = c (0, 180), xlim = c (0, 180), ratio = 1) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660","530", "450" )) +
   geom_text(aes(x = 60, y = 180, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 8.0
  )  +
  facet_wrap(~Strain, ncol = 2) +
  theme_bw() +
  labs(colour = "Growth Waveband (nm)") +
  theme(strip.text = element_blank(),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25),
        legend.position = c(0.80, 0.25),
        axis.title = element_text(hjust= 0.60, vjust = -0.2, size = 20),
        strip.text.x = element_blank(),
        axis.text = element_text(size = 15, color = "black"),)

@@

ggsave(file = file.path(PlotsPath, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

# ggsave(file = file.path(PlotsPath, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsPath, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

MED4PAR <- PURPARFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")
MED4PAR

SS120PAR <- PURPARFits %>%
   filter(Strain == "SS120",
          Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

MIT9313PAR <- PURPARFits %>%
   filter(Strain == "MIT9313",
            Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm","530 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

ggsave(file = file.path(PlotsPath, paste("MED4PAR",".png",sep = "")), plot = MED4PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsPath, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

MyWavelengths = c("WW", 660, 530, 450)
OverlayColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))

@@

MED4OverlayPlots <- PURPARFits %>%
  filter(Strain == "MED4",
          Par_ue == 90,
          O2_Category == "High" & WL == 450 & Photoperiod == 12 |
          O2_Category == "High" & WL == 530 & Photoperiod == 16 |
          O2_Category == "Intermediate" & WL == "WW" & Photoperiod == 16 |
          O2_Category == "Intermediate" & WL == 660 & Photoperiod == 12) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "waveband", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("LED emission", "Whole cell abs.", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))

>>>>

MyWavelengths = c("WW", 660, 450)

MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(450))

@@

```{r PURPARRatioPlots, fig.height= 10, fig.width= 15}

PurParPlot <- PURPARFits %>%
  filter(Par_ue %in% c(30, 90, 180)) %>%
  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313"))) %>% 
  ggplot() +
  geom_point(aes(x = Par_ue, y = Pur_ue, colour = as.factor(WL)), size = 3, alpha = 0.5) +
 geom_line(aes(x = Par_ue, y = Pur_ue,colour = as.factor(WL)), linewidth = 0.7) +
    geom_abline(slope = 1, intercept = 0, colour = "grey39", linetype = "dashed", linewidth = 1.2) +
  labs(y = "PUR (µE)" , x = "PAR (µE)") +
   scale_x_continuous(breaks=seq(0, 180, by = 30)) +
  # coord_cartesian(xlim = c (0, 180)) +
    scale_y_continuous(breaks=seq(0, 180, by = 30)) +
  coord_fixed(ylim = c (0, 180), xlim = c (0, 180), ratio = 1) +
   scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660", "450")) +
   geom_text(aes(x = 60, y = 181, label = paste(Strain), show.legend = FALSE, ),    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 8.0
  )  +
  facet_wrap(~Strain, ncol = 3) +
  theme_bw() +
  labs(colour = "Growth Waveband (nm)") +
  theme(strip.text = element_blank(),
        legend.text = element_text(size = 35),
        legend.title = element_text(size = 35),
        # legend.position = c(0.80, 0.25),
         legend.position = "top",
        axis.title = element_text(hjust= 0.5, vjust = -0.2, size = 20),
        strip.text.x = element_blank(),
        axis.text = element_text(size = 15, color = "black"),)

@@

ggsave(file = file.path(PlotsOut, paste("PurParPlot",".png",sep = "")), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

# ggsave(file = file.path(PlotsOut, paste("MED4NoPhotoPUR",".png",sep = "")), plot = MED4NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("MIT9313NoPhotoPUR",".png",sep = "")), plot = MIT9313NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("SS120NoPhotoPUR",".png",sep = "")), plot = SS120NoPhotoPUR, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

MED4PAR <- PURPARFits %>%
   filter(Strain == "MED4",
           Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")
MED4PAR

SS120PAR <- PURPARFits %>%
   filter(Strain == "SS120",
          Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
  mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

MIT9313PAR <- PURPARFits %>%
   filter(Strain == "MIT9313",
            Par_ue %in% c(30,90,180),
          deltaOD_Lmu_corr == 0 |
          deltaOD_Lmu_corr != 0 & deltaOD_LseGrowthFlag == 1) %>%
   mutate(PhotoperiodLabel_title = "Photoperiod~(h)",
         OxygenLabel = "Oxygen~Concentration~(µM)",
         WL_label_title = "Growth~Wavelength",
         ParLabel = "PAR~(µmol~photons~m^{-2}~s^{-1})",
         Par_ue = factor(Par_ue, levels = c(30, 90, 180))) %>%
  ggplot() +
  geom_point(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), size = 5, alpha = 0.5) +
 geom_line(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL), linetype = as.factor(WL)), size = 0.5) +
    geom_point(aes(x = Photoperiod, y = (deltaOD_Lmu_corr_day), colour = as.factor(WL)), size = 2.5, alpha = 0.5) +
 labs( y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "Photoperiod (h)") +
   geom_jitter(aes(x = Photoperiod, y = ReplicateMean_deltaOD_Lmu_corr_day, colour = as.factor(WL)), width = 0.1, size = 3) +
  scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", "660 nm", "450 nm" )) +
   scale_x_continuous(breaks = c(4,8, 12, 16), limits = c (4, 16)) +
  ggh4x::facet_nested(cols = vars(ParLabel, Par_ue), rows = vars(OxygenLabel, O2_uM), 
                    labeller = label_parsed) + 
 guides(linetype = "none") +
   theme_bw() +
   theme( strip.text = element_text(size = 20),
       axis.title.x.bottom = element_text(size = 30, color = "black", vjust = 1.0),
      axis.title.y = element_text(size = 30, color = "black", vjust = 1.0),
       axis.title.x.top = element_text(size = 25, color = "black", vjust = 1.0),
       axis.text.x = element_text(size = 20, color = "black", angle = 0, hjust = 0.5, vjust = 1),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
       axis.text.x.top = element_blank(),
       axis.ticks.x.top = element_blank(),
        # strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        # legend.title = element_text(size = 15),  #change legend title font size for right side legend placement
        # legend.text = element_text(size = 15),   #change legend text font size for right side legend placement
        legend.title = element_text(size = 25),  #change legend title font size
        legend.text = element_text(size = 25),   #change legend text font size
        legend.position = "top") +
  labs(color = "Growth Wavelength",
       fill = "Growth Wavelength")

@@

ggsave(file = file.path(PlotsOut, paste("MED4PAR",".png",sep = "")), plot = MED4PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("SS120PAR",".png",sep = "")), plot = SS120PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313PAR",".png",sep = "")), plot = MIT9313PAR, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

MyWavelengths = c("WW", 660, 450)
OverlayColours = c("black", w_length2rgb(660),  w_length2rgb(450))

@@

MED4OverlayPlots <- PURPARFits %>%
  filter(Strain == "MED4",
          Par_ue == 90,
          O2_Category == "High" & WL == 450 & Photoperiod == 12 |
          O2_Category == "High" & WL == 530 & Photoperiod == 16 |
          O2_Category == "Intermediate" & WL == "WW" & Photoperiod == 16 |
          O2_Category == "Intermediate" & WL == 660 & Photoperiod == 12) %>%
  mutate(WL_label = case_when(WL %in% c(450, 530, 660) ~ paste("Growth", "waveband", "=", WL, "nm", sep = " "),
        WL %in% c("WW") ~ paste("Growth", "waveband", "=", "White LED", sep = " "))) %>% 
   unnest(cols = c(PurData), names_sep = "_", keep_empty = TRUE) %>%
  pivot_longer(cols = c(PurData_PURAbsWholeCell_Norm440, PurData_AbsNorm440,  PurData_MC_NormEm), values_to = "Abs_Em_Value", names_to = "Abs_Em_Names") %>%
ggplot()+
  geom_area(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, fill = as.factor(WL)), color = "black", 
            size = 0.5, alpha = 0.7, show.legend = FALSE, 
            data = . %>% filter(Abs_Em_Names == "PurData_PURAbsWholeCell_Norm440")) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = Abs_Em_Names,  linetype = Abs_Em_Names), size = 0.85) +
  geom_line(aes(x = PurData_OlisAbs_nm, y = Abs_Em_Value, color = as.factor(WL),  linetype = Abs_Em_Names), size = 1.0, data = . %>% filter(Abs_Em_Names == "PurData_MC_NormEm")) +
  scale_color_manual(values = c(MCMIXColours, "PurData_PURAbsWholeCell_Norm440" = "black", "PurData_AbsNorm440" = "darkorchid3", "PurData_MC_NormEm" = "white")) +
  scale_linetype_manual(values = c("PurData_PURAbsWholeCell_Norm440" = "solid", "PurData_AbsNorm440" = "twodash",  "PurData_MC_NormEm" = "dotted"),
                        labels = c("Whole cell abs.",  "LED emission", "PUR")) +
  scale_fill_manual(values = MCMIXColours) +
 # guides(colour = FALSE) +
  labs(y = "Normalized Absorbance and Emission", x = "Wavelength (nm)") +
  labs(linetype = "Spectra Type")+
  scale_y_continuous(breaks=seq(0, 1.5, by = 0.25)) +
 # coord_cartesian(ylim = c (0, 0.2)) +
   facet_wrap(vars(WL),
              labeller = labeller(strain = label_value, WL = label_value, Photoperiod = label_both, Par_ue = label_both, O2_Category = label_both, Pur_ue = label_both)) +
  geom_text(aes(x = 430, y = 1.1, label = WL_label, color = as.factor(WL)), show.legend = FALSE,
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
   geom_text(aes(x = 560, y = 0.95, label = paste("PAR", "=", Par_ue, sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  geom_text(aes(x = 560, y = 0.85, label = paste("PUR", "=", Pur_ue,sep = " "), show.legend = FALSE, ),
    # parse = TRUE,
    hjust = 0,
    vjust = 1,
    size = 5.0
  )  +
  guides(color = "none") +
  theme_bw() +
 theme(strip.text = element_blank(),
       legend.background = element_rect(color = "transparent", fill = "transparent"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        # legend.position = c(0.94,0.96),
        legend.position = "top",
        axis.title = element_text(vjust = 1.0, size = 20),
        # strip.text.x = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"))
